---
title: "Machine Learning Algorithms Summary"
author: Jingyu Bao
date: 2016-11-14
output: html_notebook
---


This [Folder](./) contains all the algorithm notebooks.

To modify the automatic-load libraries, change in [.Rprofile](./.Rprofile).

## Data

To see which data are avilable in R.
```{r}
data()
```
More data can be found in package mlbench


## R packages for Machine Learning
Try to learn the package of [caret](http://topepo.github.io/caret/index.html).

- [General Caret Functions](./caret functions/Tuning Parameters.nb.html)

Use getModelinfo() function to know the details.
```{r}
svmLinearInfo <- getModelInfo("svmLinear", regex = FALSE)
svmLinearInfo[[1]] %>%
    glimpse()
```


## Supervised Learning

### Regression

- [Linear Regression](./Linear Regression/Linear Regression.nb.html)

- glmnet?

- Ensembles of Generalized Lienar Models

#### Time Series Analysis

- [Time Series General Plots](./time series/ts_plots.nb.html)

- [Time Series Train](./time series/ts_trains.nb.html)

### Classification

- [SVM](./svm/svm.nb.html)

- Adaboost

- C5.0

- eXtreme Gradient Boosting

- k-Nearest Neighbors

- [Random Forest](./Random Forest/Random forest.nb.html)

## Unsupervised Learning

- [Kmeans](./kmeans/kmeans.nb.html)

- PCA


## Parallel Computing in Caret package

If the computation takes too long, use parallel computing may speed up your algorithm

- [Parallel Computing Example](./parallel computing/parallel computing example.nb.html)


## Learning Curve

- [Learning Curve](./learning curve/Learning Curve.nb.html)

References

[caret](http://topepo.github.io/caret/index.html)
